---
title: "STAT/MATH 495: Problem Set 01"
author: "Syed Abbas Shah"
date: "2017-09-07"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    collapsed: false
    smooth_scroll: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width=8, fig.height=4.5)

# Load packages
library(tidyverse)
library(mosaic)
library(knitr)
library(readr)
```


```{r}
train <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/train.csv")
test <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/test.csv")
submission <- read_csv("https://rudeboybert.github.io/STAT495/static/Titanic/gender_submission.csv")

glimpse(train)
glimpse(test)
glimpse(submission)



test %>% 
  left_join(submission, by="PassengerId") %>% 
  select(PassengerId, Sex, Survived)
```
That's a simple model where only sex is considered when deciding who survived on the Titanic.

We can make more complicated models obviously. For now, I'll just look at selecting one more variable and looking at Survival based on that and Sex.
```{r}
model2 <- lm(train$Survived~train$Sex + train$Age + train$Fare + train$Pclass + train$SibSp)
summary(model2)
```

Let's Look at Pclass.

```{r}
table(train$Survived,train$Sex,train$Pclass)
```

Let's assume that everyone in first class and women in second class survived, whereas everyone else perished.

```{r}
x<-test %>% 
  left_join(submission, by="PassengerId") %>% 
  select(PassengerId, Pclass,Sex, Survived)
x2<-ifelse(x$Pclass==1,x$Survived <- 1, ifelse(x$Pclass==2 & x$Sex=="female", x$Survived<-1, 0))

x2<-as.data.frame(x2)

submission$Survived<- x2$x2
submission$Survived<-as.integer(submission$Survived)
mean(train$Survived); mean(submission$Survived)
glimpse(submission)
```

